\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{ragged2e}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubheadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubheadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, noitemsep, label={$\cdot$}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Kim Javier} \\ \vspace{1pt}
    Technical Leader | Project Manager | DevOps \& Full-Stack Developer | Cloud, Security \& Network Automation \\ \vspace{1pt}
    \small 📍 Philippines | \href{https://sargo.ph}{sargo.ph} | \href{mailto:kim.javier@example.com}{kim.javier@example.com} | \href{https://github.com/kimjavier}{GitHub: github.com/kimjavier}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \resumeItemListStart
    \resumeItem{Hands-on technical leader and project manager with expertise in full-stack development, DevOps, cloud infrastructure, network automation, and enterprise security. I build and lead engineering teams to deliver robust, automated, and secure systems for industries including EV platforms and intercloud services. Skilled in bridging software development, infrastructure, and network operations, with a focus on scalable, high-performance, and maintainable applications.}
  \resumeItemListEnd
  \vspace{-5pt}
  \textbf{Core Competencies:}
  \resumeItemListStart
    \resumeItem{\textbf{Infrastructure \& Cloud Automation:} AWS, OVH, Terraform, Docker/Kubernetes, IAM, SOPS, HashiCorp Vault}
    \resumeItem{\textbf{Full-Stack \& Microservices:} NestJS, React, Node.js, PostgreSQL, Microfrontend architectures}
    \resumeItem{\textbf{Network Automation \& Connectivity:} Cisco NSO, NetBox, Megaport, Equinix}
    \resumeItem{\textbf{Enterprise Security:} OIDC/OAuth2, Keycloak, SSO, IAM, Vault, SOPS}
    \resumeItem{\textbf{Testing \& Reliability:} Stress/load testing, integration testing, Pact, WireMock}
    \resumeItem{\textbf{CI/CD \& DevOps:} GitHub Actions, GitLab pipelines, production deployments}
    \resumeItem{\textbf{UI/UX \& Documentation:} Figma, developer-friendly specifications}
  \resumeItemListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubheadingListStart
    \resumeSubheading
      {Founder / Technical Lead – Tournament Bracket App}{2024–Present}
      {}{}
      \resumeItemListStart
        \resumeItem{Designed and launched a fully automated tournament bracket platform with dynamic scheduling and player management.}
        \resumeItem{Built a microservices backend (NestJS + PostgreSQL) and a modern React frontend.}
        \resumeItem{Implemented CI/CD pipelines via GitHub Actions, reducing deployment time from hours to minutes.}
        \resumeItem{Integrated user login with Google authentication for secure access.}
        \resumeItem{Delivered a reliable platform supporting continuous tournaments and high concurrency.}
      \resumeItemListEnd
    \resumeSubheading
      {EV Industry – Infrastructure \& Systems Architect}{}
      {}{}
      \resumeItemListStart
        \resumeItem{Architected scalable EV backend platforms on AWS and OVH, handling thousands of concurrent connections.}
        \resumeItem{Automated provisioning, scaling, and identity/access management across multiple cloud environments.}
        \resumeItem{Implemented stress/load testing to validate performance and reliability.}
        \resumeItem{Managed secrets and secure configuration using SOPS and Keycloak.}
      \resumeItemListEnd
    \resumeSubheading
      {Legacy System Modernization \& Intercloud Migration}{}
      {}{}
      \resumeItemListStart
        \resumeItem{Migrated legacy React apps to the latest versions, improving maintainability and developer velocity.}
        \resumeItem{Transformed monolithic frontends into microfrontend architecture, enabling independent feature deployment.}
        \resumeItem{Implemented intercloud infrastructure with Terraform for seamless multi-cloud operations.}
        \resumeItem{Built integration contract testing systems using Pact, reducing integration failures by 70\%.}
        \resumeItem{Integrated enterprise authentication and authorization using OIDC, OAuth2, Cognito, SSO, and Keycloak.}
      \resumeItemListEnd
    \resumeSubheading
      {Network Services Automation – Cisco NSO \& Vendor Integration}{}
      {}{}
      \resumeItemListStart
        \resumeItem{Designed backend automation systems using Cisco NSO, integrating Megaport virtual connectivity and Equinix data centers.}
        \resumeItem{Maintained network inventory and orchestration with NetBox.}
        \resumeItem{Ensured secure vendor API authentication and automated workflows.}
      \resumeItemListEnd
  \resumeSubheadingListEnd

%-----------PROJECTS-----------
\section{Projects / Featured Work}
  \resumeItemListStart
    \resumeItem{Tournament Bracket Platform – Live at \href{https://sargo.ph}{sargo.ph} (Google login)}
    \resumeItem{EV Backend Platforms – Scalable, stress-tested systems on AWS and OVH}
    \resumeItem{Legacy React Migration \& Microfrontend Implementation}
    \resumeItem{Network Automation Backend – Cisco NSO integration with Megaport \& Equinix}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubheadingListStart
    \resumeSubheading{[Your Degree]}{[Year]}
      {[Your University]}{}
      \resumeItemListStart
        \resumeItem{(optional if you want to include)}
      \resumeItemListEnd
  \resumeSubheadingListEnd

%-----------SKILLS-----------
\section{Skills}
  \resumeItemListStart
    \resumeItem{Project Management / Agile / Scrum}
    \resumeItem{Full-Stack Development: NestJS, React, Node.js, TypeScript, TypeORM, PostgreSQL}
    \resumeItem{Cloud \& Infrastructure: AWS, OVH, Terraform, Kubernetes, Docker, IAM}
    \resumeItem{Network Automation: Cisco NSO, NetBox, Megaport, Equinix}
    \resumeItem{Security \& Identity: Cognito, OIDC, OAuth2, SSO, Keycloak, SOPS, HashiCorp Vault}
    \resumeItem{Testing \& Reliability: Simulators, Pact, WireMock, Stress/Load Testing}
    \resumeItem{CI/CD: GitHub Actions, GitLab, Production Pipelines}
    \resumeItem{UI/UX \& Documentation: Figma, Developer-Friendly Specifications}
  \resumeItemListEnd

\end{document}
